Useful R tidbits: Machine Learning

### 2022-02-08 _academics/ms797-useful-r-tidbits/ms797-useful-r-tidbits.Rmd
build
Link to ps753 tidbits page, title change

---
title: "Useful R tidbits"
description: |
  Tasty R snacks that do useful things
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-06
output:
  distill::distill_article:
    self_contained: false
    toc: true
preview: ISLR-cover.png
---

@@

<p style="background: #eee">
Academics &gt; [MS797](../ms797/index.html)
&gt; Useful R tidbits
</p>

>>>>

---
title: "Useful R tidbits: Machine Learning"
description: |
  Tasty R snacks that do useful things in Machine Learning
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-06
output:
  distill::distill_article:
    self_contained: false
    toc: true
preview: ISLR-cover.png
---

@@

<p style="background: #eee">
[<i class="fas fa-home"></i>](/) &gt; Academics &gt; [MS797](../ms797/index.html)
&gt; Useful R tidbits
</p>

This document contains R snippets pertaining to work in the [Machine Learning class](../ms797/index.html). There is also one for the [Social Networks class](../px753/index.html).
